Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-29 ms.tex
beta footnote

We fix $\beta = 2$ but find that our results are not overly sensitive to
the properties of the gas flow on radial scales $\gtrsim r_b$ for values of
$\beta\gsim 1.5$, which characterize most of the \citet{LauerFaber+:2007a} sample.  The
presence of the break radius $r_{b}$ is, however, necessary to obtain
a converged steady state for some regions of our parameter space.  We
consider solutions calculated for up to four values of $\rb$: 50 pc,
100 pc, 200 pc, and 400 pc, motivated by the range of break radii from
the \citet{LauerFaber+:2007a} sample.\footnote{For the core galaxies
  the break radius follows the scaling relationship $\rb\sim 106 \,
  (\Mbheight)^{0.39}$ pc, with scatter of approximately one dex.  Most
  the cusp galaxies have $\rb$ between 100 and 1000 pc, and lack a
  clear trend with $\Mbh$.}  We neglect values of $r_b$ which would
give unphysically large bulges for a given $\Mbh$.
% In practice we calculate solutions for a
%range of $\rb$ only in cases when its precise value is expected to
%have a significant affect on the solution, in particular for high SMBH
%masses and low heating rates, for which the stagnation radius
%approaches large radii. 
%We also neglect values of $r_b$ which would
%give unphysically large bulges for a given $\Mbh$.

>>>>

We fix $\beta = 2$ but find that our results are not overly sensitive
to the properties of the gas flow on radial scales $\gtrsim r_b$ for
values of $\beta\gsim 1.5$, which characterize most of the
\citet{LauerFaber+:2007a} sample\footnote{The median $\beta$ in the
  \citet{LauerFaber+:2007a} sample is 1.39 (1.64) for core (cusp)
  galaxies}.  The presence of the break radius $r_{b}$ is, however,
necessary to obtain a converged steady state for some regions of our
parameter space.  We consider solutions calculated for up to four
values of $\rb$: 50 pc, 100 pc, 200 pc, and 400 pc, motivated by the
range of break radii from the \citet{LauerFaber+:2007a}
sample.\footnote{For the core galaxies the break radius follows the
  scaling relationship $\rb\sim 106 \, (\Mbheight)^{0.39}$ pc, with
  scatter of approximately one dex.  Most the cusp galaxies have $\rb$
  between 100 and 1000 pc, and lack a clear trend with $\Mbh$.}  We
neglect values of $r_b$ which would give unphysically large bulges for
a given $\Mbh$.
% In practice we calculate solutions for a
%range of $\rb$ only in cases when its precise value is expected to
%have a significant affect on the solution, in particular for high SMBH
%masses and low heating rates, for which the stagnation radius
%approaches large radii. 
%We also neglect values of $r_b$ which would
%give unphysically large bulges for a given $\Mbh$.
